Our peculiar motion across the Universe

### 2019-07-02 paper/main.tex
edit

We select all halos with a maximum circular velocity larger than $xx$\kms.

>>>>

We start by selectin all halos with a maximum circular velocity larger
than $200$ \kms.
Then we proceed to use these halos to find what we call an Isolated Pair
(IP).
IPs are two halos, $A$ and $B$, that do not have any other third halo
closer than the $AB$ separation; in other words in IPs the two halos
are mutually its closest neighbor.
